---
title: "PLAY/LEGO report"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    code_folding: hide
    df_print: paged
params: 
  db_account: email@domain.com
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pilot.vol.id <- 444
nichd.vol.id <- 254
lego.vol.id <- 563
library(tidyverse)
library(databraryapi)
library(ggplot2)
login_db(params$db_account)
```

# PLAY pilot summary data

## Demographic summary

```{r gest-age-hist}
pilot_demog <- summarize_demog(vol.id = pilot.vol.id, return.df = TRUE)

pilot_demog %>% 
  ggplot(.) +
  aes(x = participant.gestational.age, y = participant.birth.weight, color = participant.race) +
  geom_point()
```

```{r age-by-gender}
pilot_demog %>%
  ggplot(.) +
  aes(x = age.weeks, fill = participant.gender) +
  geom_histogram()
```

## Parent-report variables

```{r}
survey.session.id <- 26295
list_assets_in_session(vol.id = pilot.vol.id, session.id = survey.session.id) %>%
  select(asset.name, asset.type, asset.id)
```

```{r}
(csv_fl <- list.files('csv', '\\.csv$', full.names = TRUE)) 
```

```{r}
lang_exp <- read_csv(csv_fl[1])
str(lang_exp)
```

```{r}
play.palette <- scale_fill_manual(values=c("blue2", "firebrick2", "chartreuse2", "darkorchid2"))

play.theme <-   
  theme_classic() +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        legend.text = element_text(size = rel(1.2)),
        axis.title = element_text(size = rel(1.5), face ="bold"),
        axis.text.x = element_text(size = rel(1.2)),
        axis.text.y = element_text(size = rel(1.2)),
        axis.line = element_blank(),
        axis.title.y = element_blank())

lang_exp %>%
  ggplot(.) +
  aes(x = language) +
  facet_grid(exposure_context ~ .) +
  geom_histogram(stat='count') +
  play.theme
```

```{r}
loco_onset <- read_csv(csv_fl[3])
str(loco_onset)
```
```{r}
loco_onset %>%
  gather(key = milestone, value = age.mos, hkcrawl_onset_mos, walk_onset_mos) %>%
  mutate(milestone = factor(milestone, labels = c("crawl", "walk"))) %>%
  # arrange(desc(age.mos)) %>%
  ggplot() +
  aes(x = age.mos, y = id) +
  geom_point(aes(shape = milestone, color = milestone)) +
  geom_line(aes(group = id)) +
  xlab("Age (months)") +
  geom_rug(aes(x = age.mos, group = milestone, color = milestone),
           sides = "b") +
  play.theme
```


# LEGO

```{r}
lego_demog <- databraryapi::summarize_demog(vol.id = lego.vol.id, return.df = TRUE)

lego_demog %>%
  ggplot(.) +
  aes(y = age.weeks, x = group.name) +
  geom_boxplot()
```

```{r, race-by-gender}
lego_demog %>%
  ggplot(.) +
  aes(participant.gender, fill = participant.gender) +
  facet_grid(participant.race ~ group.name) +
  geom_bar()
```

# Individual-specific reports from PLAY

Let's focus on [NYU_019 in volume 254](https://nyu.databrary.org/volume/254/slot/14514/-)

## Videos

### [Child view](https://nyu.databrary.org/slot/14514/69908000,73576800/asset/61054/download?inline=true)

<video controls>
  <source src="https://nyu.databrary.org/slot/14514/69908000,73576800/asset/61054/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>

### [Experimenter view](https://nyu.databrary.org/slot/14514/69908000,73623840/asset/61086/download?inline=true)

<video controls>
  <source src="https://nyu.databrary.org/slot/14514/69908000,73623840/asset/61086/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>

## Assets in session

```{r}
vol_254_assets <- list_assets_in_session(254, 14514)
vol_254_assets %>%
  select(., asset.name, asset.type, asset.id)
```

## Process Datavyu

### Download
```{r}
unlink('tmp', recursive = TRUE)
dv_info <- filter(vol_254_assets, asset.type == "Datavyu")
dv_dir <- download_datavyu(vol.id = 254, session.id = 14514, asset.id = dv_info$asset.id)
```

### Extract codes and code definitions

Now, let's extract the components of the Datavyu file, including the code definitions.

```{r}
extract_dv(in.dir = dv_dir, auto.write.over = TRUE)
dv_to_csv(dv.dir = dv_dir)
list.files('tmp')
```

Next, we can load the Datavyu file as a csv.

```{r}
dv_fn <- list.files('tmp', '\\.csv$', full.names = TRUE)
vol_254_14514 <- read_csv(dv_fn)
str(vol_254_14514)
```

```{r}
vol_254_14514
```

```{r}
extract_dv_code_defs(in.dir = 'tmp')
code_fn <- list.files('tmp', '-code-defs\\.csv$', full.names = TRUE)
vol_254_14514_codes <- read_csv(code_fn)
vol_254_14514_codes
```

### Visualize clips from specific codes

Let's look at the baby's locomotion (`babyloc`) code.

```{r}
(babyloc <- filter(vol_254_14514, code == 'babyloc'))
# Surrounding assignment w/ parentheses also prints out the assigned value.)
```

Let's look at the code values.

```{r}
unique(babyloc$code.value) 
```

Focus on holds `h` because there are fewer of them.

```{r}
# Select segments for this code
(babyloc_segs <- dplyr::filter(babyloc, code.value == 'h'))
```

### Download video segment corresponding to one or more of these codes

Let's pick the second segment just for fun.

```{r}
# What is the segment range for the video?
seg_range <- get_asset_segment_range(vol.id = 254, session.id = 14514, asset.id = 61054)
start_ms <- HHMMSSmmm_to_ms(babyloc_segs$onset[2]) + seg_range[1]
end_ms <- HHMMSSmmm_to_ms(babyloc_segs$offset[2]) + seg_range[1]
selected_seg <- paste0(start_ms, ",", end_ms)
```

Now download the video.

```{r}
#download_video(254, 14514, 61054, out.dir = 'tmp', segment.id = selected_seg)
```

And see if we can display video or if needed, [go to it on Databrary](https://nyu.databrary.org/slot/14514/71873879,71875206/asset/61054/download?inline=true).

<video controls>
  <source src="https://nyu.databrary.org/slot/14514/71873879,71875206/asset/61054/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>
